Kronos \& Krios: TBD

### 2017-05-04 paper/ms.tex
star names fixed

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
\newcommand{\sunanalog}{\text{HD 240429}}
\newcommand{\bizarreone}{\text{HD 240430}}

@@

\title{A pair of co-moving, Sun-like stars with different chemical abundances:\\
       a possible signature of copious rocky accretion (needs work)}

@@

@@

Given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We compared the measured $\log(g)$ and $T_\mathrm{eff}$ to \project{MIST} isochrones at two
different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
The two most consistent isochrones at $28$~Myr and $2$~Gyr based on $\chi^2$ values
are plotted in Figure~\ref{fig:isochrones}.
For \sunanalog\ ($\feh = 0.01$), the most consistent isochrone is that for
an age of $2$~Gyr and $\feh = 0.2$.
The $\log(g)$ values of the two stars, especially of \bizarreone\, seem to suggest
that they could be at the end of the pre-main sequence phase.
However, an age of $28$~Myr for \sunanalog\ is in tension with the larger age ($800$~Myr)
inferred from its $\elem{Li}$ abundance.
Also, at such a young age, we may expect to see infrared excess from a circumstellar disk or
X-ray emission from magnetic activity. 
However, the spectral energy distributions of the two stars based on
\project{Tycho-2}, \tmass, \project{WISE} photometry (\todo{CITE}) are consistent with blackbody,
and no relatable X-ray point sources are found in the \project{ROSAT} All-Sky Survey
around the two stars,
On the other hand, the most consistent main sequence age ($2$~Gyr) also is in tension with
its relatively high $\elem{Li}$ abundance, not to mention with the $\log(g)$ of \bizarreone\
if the two stars should have the same age.

>>>>

% define macros for text
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\tmass}{\project{\acronym{2MASS}}}
\newcommand{\documentname}{Article}
\newcommand{\sectionname}{Section}
\newcommand{\figname}{Figure}
\newcommand{\eqname}{Equation}
\newcommand{\dr}{\acronym{DR1}}
\newcommand{\tgas}{\acronym{TGAS}}
\newcommand{\etal}{\textit{et al}.}
\newcommand*\elem[1]{\ensuremath{\mathrm{#1}}}
\newcommand*\elemH[1]{\ensuremath{[\mathrm{#1}/\elem{H}]}}
\newcommand*{\feh}{\ensuremath{\elemH{Fe}}}
\newcommand{\sunanalog}{\text{Krios}}
\newcommand{\bizarreone}{\text{Kronos}}

@@

\title{Kronos \& Krios: TBD}

@@

Wide binaries are valuable tools for studying star and planet formation as well as
Galactic dynamics and chemical evolution.
They tidally disrupt.

@@

Given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We compared the measured $\log(g)$ and $T_\mathrm{eff}$ to \project{MIST} isochrones at two
different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
The ages most consistent with $\log(g)$ and $t_\mathrm{eff}$ for
\sunanalog\ and \bizarreone\ using the isochrones of corresponding metallicities
is $\approx 4$~Gyr and $\approx 5.6$~Gyr respectively, based on $\chi^2$ values.
This is in tension with the relatively high $\elem{Li}$ abundance in both stars.
Even for \sunanalog\, a $\elem{Li}$ abundance of 2.25 is unusually high for a sunlike star with
similar ages.

are plotted in Figure~\ref{fig:isochrones}.
For \sunanalog\ ($\feh = 0.01$), the most consistent isochrone is that for
an age of $2$~Gyr and $\feh = 0.2$.
The $\log(g)$ values of the two stars, especially of \bizarreone\, seem to suggest
that they could be at the end of the pre-main sequence phase.
However, an age of $28$~Myr for \sunanalog\ is in tension with the larger age ($800$~Myr)
inferred from its $\elem{Li}$ abundance.
Also, at such a young age, we may expect to see infrared excess from a circumstellar disk or
X-ray emission from magnetic activity. 
However, the spectral energy distributions of the two stars based on
\project{Tycho-2}, \tmass, \project{WISE} photometry (\todo{CITE}) are consistent with blackbody,
and no relatable X-ray point sources are found in the \project{ROSAT} All-Sky Survey
around the two stars,
On the other hand, the most consistent main sequence age ($2$~Gyr) also is in tension with
its relatively high $\elem{Li}$ abundance, not to mention with the $\log(g)$ of \bizarreone\
if the two stars should have the same age.
